Growth Dynamics of the Independent Gametophytes of *Pleurosoriopsis makinoi*

### 2022-10-08 ms.Rmd
Fix _targets workflow

# Load objects from drake workflow into memory
loadd(selected_vars)
loadd(combined_morph)
loadd(daily_microclimate)
loadd(t_test_results)
loadd(paired_microclimate)
loadd(nested_paired_microclimate)
loadd(combined_monthly_morph)
loadd(linear_model_results)
loadd(gameto_size)
```

>>>>

# Load objects from drake workflow into memory
tar_load(c(
  selected_vars,
  combined_morph,
  daily_microclimate,
  t_test_results,
  paired_microclimate,
  nested_paired_microclimate,
  combined_monthly_morph,
  linear_model_results,
  gameto_size)
)
```
